A 38 Million Year Old Mini-Neptune in the Kepler Field

### 2021-09-21 paper/ms.tex
update ms

The amplitude of both the spot-induced trend and
the jitter are larger than recent comparable measurements
in systems such as AU~Mic
\citep{palle_transmission_2020}, DS~Tuc
\citep{montet_young_2020,zhou_well_2020} and TOI~942
\citep{wirth_2021_toi942}.  One possible explanation for the jitter is that it is
astrophysical in origin, and that it is caused by some novel process
operating on the surface of Kepler 1627A.  Another possibility is that our RV
analysis underestimates the measurement uncertainties; the S/N per
resolution element for each of our spectra (70 to 80) was somewhat low
due to the observing requirements, and the star is a rapid rotator.
We currently favor the latter possibility.  Observations at higher
precision remain worthwhile to clarify the orbital geometry of \pn.

>>>>

The amplitude of both the spot-induced trend and the jitter are larger
than recent comparable measurements in systems such as AU~Mic
\citep{palle_transmission_2020}, DS~Tuc
\citep{montet_young_2020,zhou_well_2020} and TOI~942
\citep{wirth_2021_toi942}.  One possible explanation for the jitter is
that it is astrophysical in origin, and that it is caused by some
novel process operating on the surface of Kepler 1627A.  Another
possibility is that our RV analysis underestimates the measurement
uncertainties; the S/N per resolution element for each of our spectra
(70 to 80) was moderated by the observing requirements, and the rapid
rotation of the star could affect the velocity extraction.
Observations at higher precision are necessary to distinguish these
two possibilities, and remain worthwhile as a means toward clarifying
the orbital geometry of \pn.
